Long--term perspectives of social inequality in mortality among adults and elderly in northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-06-08 abo.Rnw
first commit (from copy of 'Umeå.Rnw')

\title{Long--term perspectives of social inequality in mortality among adults and elderly in
  northern  Sweden 1851--2013\footnote{Session "Health and Mortality in Arctic Populations" at The Ninth International Congress on Arctic Social Sciences (ICASS IX) June 10, 2017, Umeå}
}

@@

\author{Sören Edvinsson and Göran Broström \\
Centre for Ageing and Demographic Research, Umeå University}

>>>>

\title{Long--term perspectives of social inequality in mortality among adults and elderly in
  northern  Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}
}

@@

\author{Sören Edvinsson and Göran Broström \\
Centre for Ageing and Demographic Research \\
Umeå University, Umeå, Sweden}
